### 2012-12-10 articles/TechCon/paper.tex
SBRC 2013 paper complete first version

%Service Choreography Simulator with QoS compisition
  %QoS Service choreography support through Simulator
  %QoS support in service choreography through a simulator engine
\tctitle{
  A simulator for QoS Service choreography support
}

@@

 Service choreography allows the composition of services in a collaborative way, because of global description and descentralized 
coordination using interactions P2P among participants. However, since   infraestructures and implementations aren't mature enough
 to enact choreographies, then to evaluate and analyse how the environment affects the QoS requirements and composition behavior 
into a choreography is a difficult task. To be able to do so, we propose to develop a choreography simulator in order to simulate 
enacting of choreographies.

 In this work, we also  propose a QoS model for implementing  on the choreography simulator taking  into account QoS composition, infraestructure
 and environment aspects.  Furthermore, we adopted a choreography scenario about Content Delivery Network (CDN) providing
 streaming multimedia objects.

@@

Among the various methods to compose services, Web services choreography is an efficient way to implement inter-organizational business
 processes, as the participants' business interactions are mutually independent (autonomous and heterogeneous) \cite{Telang2011}. A service
 choreography is a description of peer to peer interactions among existing services, i.e., in this model there isn't the role of 
 a central controller. The various services communicate with each other similarly to what occurs in a P2P applications \cite{Barker2009}.

Due to the increasing number of devices joining the Internet,
a centralized approach like an orchestration may not be sufficiently
scalable in terms of network bandwidth to deal with the
ever escalating number of devices and services that may be
available. Within such a scenario, a decentralized approach,
like choreographies, may turn out to be more capable of
dealing with such high complexity (trecho do artigo do Felipe e Eduardo, dá para tirar ele).

 During the enactment of  services choreographies, the state of network elements (devices and links) plays a fundamental role. There must be guarantees 
 of Quality of Service - QoS so that there are advantages of using a decentralized business model. A common method to define
 guarantees between a service provider and a client (which may also be a service) is by means of a Service Level Agreement - SLA. After
 the choreography be specified,  constraints of QoS between each participant must be defined through SLAs \cite{Rosenberg2007}. To meet the SLA 
 agreements there must be some mechanism for management at runtime. This mechanism must involve monitoring, control and  
 decisions against violations or degradation of service quality. All the concern about guarantee of the QoS requirements of participants comes 
 from the fact that the QoS of composite service, represented by the choreography, depends directly on the QoS of the separate services.

% To reduce the number of SLA violations and the corrective measures to fulfill the QoS requirements during the enactment of choreographies, 
% the detection of non-functional failures in early stages of the development of the choreography can be employed.

Currently, to implement and enact a real service choreography is still difficult because of immature technology support, especially
by lack of Choreography aware engine execution~\cite{Kopp2010}. Then, performance evaluations, QoS measurements, QoS requirements
 establishment, monitoring, and so on, aren't very developed.

@@

The objective of our work is to develop a simulator in order to enact services choreographies  and enable QoS support taking into account 
the infrastructure and  environment aspects. For achieve this, we  use a QoS model about  service, message and communication attributes involved 
in a service choreography.  Moreover, to attest the efficacy of our simulator we adopt a choreography scenario about Content Delivery Network (CDN) providing
 streaming multimedia objects~\cite{Buccafurri2008a}. %%and we show some experimental results, or performance evaluation using our simulator

Based on ~\cite{Pandey2010}  and ~\cite{Looker} works, we propose a model QoS in three aspects: (a)service ,(b) message and (c) communication. The table ~\ref{table:QoSmodel}
 shows the QoS model composed by QoS attributes, metrics and respective failure types, that our simulator should support.

@@

Figure~\ref{figure:scenario} shows the reference scenario~\cite{Buccafurri2008a} : a user requires, and eventually receives, a complex service 
managed through a choreography of different Web-Services, one of which (WS3 in the figure) controls the provisioning of streaming content. WS1
and WS2 show that several Web-Services are internally orchestrated. Such a scenario is used for assessment of choreography simulator.

%; in the rest of the paper our reference point will be WS1.
%

@@

The SimGrid framework [3] is a simulation-based framework for evaluating cluster, grid and P2P mechanisms. SimGrid uses tasks to
 perform the simulation. Such tasks have an intrinsic cost to be transmitted over the network and an execution cost. Resources
 are described through an XML file in which it is possible to list available resources and their characteristics such as computing power, as well as available
links and routes to other resources. In another XML file the deployment of the simulated entities is described, ie,
where each simulated entity, also referred to as a Process, is deployed. Since the SimGrid allows the simulation of
distributed environments, we used it as the base to implement our simulator.

Regarding the software,  
...

@@

\section*{Current status}
%Nós temos desenvolvido um simulador inicial  para realizar o ``enactment'' de coreografias, mas 
%para nossos objetivos adicionamos suporte de composição de QoS e infraestrutura de comunicação.
We have developed a simulator to perform the `` initial'' enactment of choreography, but
our objectives for added support of QoS composition and communication infrastructure.

In this research project we are interested in the .... Our current efforts are
focused on the quantitative analysis. We are evaluating the
performance based on simulations, particularly interested in studying the effects of QoS composition on throughput
 of services and  networks aspects such as latency and bandwidth.

@@

>>>>

%Service Choreography Simulator with QoS compisition
  %QoS Service choreography support through Simulator
  %QoS support in service choreography through a simulator engine
\tctitle{
  A Simulator for QoS Service Choreography support
}

@@

 Service choreography allows the composition of services in a collaborative way, because of global description and descentralized 
coordination using interactions P2P among participants. However, since   infraestructures and implementations aren't mature enough
 to enact choreographies,
%then to evaluate and analyse how the environment affects the QoS requirements and composition behavior 
%into a choreography is a difficult task. To be able to do so, we propose to develop a choreography simulator in order to simulate 
%enacting of choreographies.  
it is difficult to evaluate and analyse the fulfillment of QoS requirements when using
choreographies. In this paper we propose a simulator of choreographies in order to evaluate parameters of QoS. We also
propose a QoS model.

% In this work, we also  propose a QoS model for implementing  on the choreography simulator taking  into account QoS composition, infraestructure
% and environment aspects.  Furthermore, we adopted a choreography scenario about Content Delivery Network (CDN) providing
% streaming multimedia objects.

@@

Due to the increasing number of devices joining the Internet, a centralized approach like an orchestration may not be sufficiently
scalable in terms of network bandwidth to deal with the ever escalating number of devices and services that may be 
available. Within such a scenario, a decentralized approach, like choreographies, may turn out to be more capable of
dealing with such high complexity [3].

%Among the various methods to compose services,
 Web services choreography is an efficient way to implement inter-organizational business
 processes, as the participants' business interactions are mutually independent (autonomous and heterogeneous). A %\cite{Telang2011}. A 
 choreography is a description of peer to peer interactions among existing services, i.e., in this model there isn't the role of 
 a central controller, unlike of orchestration and current ESB\footnote{ESB: Enterprise Service Bus} technologies.  % tip: We could add a reference to ESB technology, just to illustrate, since it is often used by current production systems (market), and it has a single failure point;
 The various services communicate with each other directly ~\cite{Barker2009}. %similarly to what occurs in a P2P applications \cite{Barker2009}.

 During the enactment of  services choreographies, the state of network elements (devices and links) plays a fundamental role. There must be guarantees 
 of Quality of Service - QoS so that there are advantages of using a decentralized business model. A common method to define
 guarantees between a service provider and a client (which may also be a service) is by means of a Service Level Agreement - SLA.

%After  the choreography be specified,  constraints of QoS between each participant must be defined through SLAs \cite{Rosenberg2007}. To meet the SLA 
% agreements there must be some mechanism for management at runtime. This mechanism must involve monitoring, control and  
% decisions against violations or degradation of service quality. All the concern about guarantee of the QoS requirements of participants comes 
% from the fact that the QoS of composite service, represented by the choreography, depends directly on the QoS of the separate services.

%% To reduce the number of SLA violations and the corrective measures to fulfill the QoS requirements during the enactment of choreographies, 
%% the detection of non-functional failures in early stages of the development of the choreography can be employed.

Currently, to implement and enact a real service choreography is still difficult due immature technology support, especially
by lack of choreography aware engine execution~\cite{Kopp2010}. Thus, mechanisms to define QoS measurements, QoS requirements
 establishment, monitoring, and so on, aren't well developed to choreographies.

@@

The objective of our work is to develop a simulator in order to enact services choreographies  and enable QoS support taking into account 
the infrastructure and  environment aspects. To achieve it, we  use a QoS model over  service, message and communication attributes involved 
in a service choreography.

% Moreover, to attest the efficacy of our simulator we adopt a choreography scenario about Content Delivery Network (CDN) providing
% streaming multimedia objects~\cite{Buccafurri2008a}. %%and we show some experimental results, or performance evaluation using our simulator

Based on ~\cite{Pandey2010}  and ~\cite{Looker} works, we propose a model QoS in three aspects: (a) service , (b) message and (c) communication. 
The table~\ref{table:QoSmodel} shows the QoS model composed by QoS attributes, metrics and respective failure types, that our simulator should support.

@@

To implement an entire simulator is a very complex task, due that,  we decided to use an existing simulador as the base of
our simulator.[EH] Could be better to explicit show which one has been chosen in this paragraph.

The SimGrid framework~\cite{Casanova2008} is a simulation-based framework for evaluating cluster, grid and P2P mechanisms. SimGrid uses tasks to
 perform the simulation. Such tasks have an intrinsic cost to be transmitted over the network and an execution cost. Resources
 are described through an XML file in which it is possible to list available resources and their characteristics such as computing power, as well as available
links and routes to other resources. In another XML file the deployment of the simulated entities is described, i.e,
where each simulated entity, also referred to as a Process, is deployed.

Since the SimGrid allows the simulation of distributed environments, we used it as the base to implement our simulator.

To attest the efficacy of our simulator we adopt a choreography scenario about Content Delivery Network (CDN)
providing streaming multimedia objects ~\cite{Buccafurri2008a}. The Figure~\ref{figure:scenario} shows the reference
 scenario~\cite{Buccafurri2008a} : a user requires, and eventually receives, a complex service 
managed through a choreography of different Web-Services, one of which ($WS_3$ in the figure) controls the provisioning of streaming content. $WS_1$
and $WS_2$ show that several Web-Services are internally orchestrated. Such a scenario is used for assessment of choreography simulator.

%; in the rest of the paper our reference point will be WS1.

@@

@@

\section*{Current status}
%Nós temos desenvolvido um simulador inicial  para realizar o ``enactment'' de coreografias, mas 
%para nossos objetivos adicionamos suporte de composição de QoS e infraestrutura de comunicação.
Since there was no simulator systems for service choreographies, we have developed a initial simulator to compare the performance
 of an orchestrations and a choreography \cite{Guimaraes2012}. There, choreographies revealed to be a better choice with regard to performance
 and to perform the enactment of choreographies. Currently, we are evaluating the performance based on simulations,
 particularly interested in studying the effects of QoS composition on throughput of services and networks aspects
 such as latency and bandwidth. Furthermore, we are developing the simulator with focus in choreography enactment and QoS support.

%In this research project we are interested in the .... Our current efforts are
%focused on the quantitative analysis. We are evaluating the
%performance based on simulations, particularly interested in studying the effects of QoS composition on throughput
% of services and  networks aspects such as latency and bandwidth.

@@

As a next step we will compare the results obtained in our simulator with measurements of a real choreography. 
Also, we will develop a monitoring module in order to perform  QoS measurements, QoS aggregation, and so on. In this way, we will
have the infrastructure for achieving SLA establishment, QoS violation detection, and other QoS issues, on service choreographies.

%our objectives are to develop focus in choreography add support of QoS composition
% and communication infrastructure. For this reason,
